\section{Potential for undefined behavior}

In this section we analyze some examples of possible undefined behavior.

\subsection{Example 1}

In~\cite{p1321r0} an example provided by Herb Sutter and
prototyped by Peter Dimov (see at
\url{https://godbolt.org/g/7TP7Mt}) with simulated contracts 
is presented.

Essentially this example translated into contracts syntax would be:

\begin{lstlisting}
void f(int x) [[expects audit: x==2]]
{
  printf("%d\n", x);
}

void g(int x) [[expects: x>=0 && x<3]]
{
  extern int a[3];
  a[x] = 42;
}

void foo();
void bar();
void baz();

void h(int x) [[expects: x>=1 && x<=3]]
{
  switch(x) {
    case 1: foo(); break;
    case 2: bar(); break;
    case 3: baz(); break;
  }
}

void test()
{
  int val = std::rand();

  try { f(val); /*...*/ } catch(...) { /*...*/ }
  try { g(val); /*...*/ } catch(...) { /*...*/ }
  try { h(val); /*...*/ } catch(...) { /*...*/ }
}
\end{lstlisting}

\subsubsection{Current status}

With the current definition of contracts, compiling the code with the build mode
set to \textmark{audit} is not problematic. The precondition at \cppid{f()} is
checked and it can be assumed to be true in next calls. Then, calls to \cppid{g()}
and \cppid{h()} can optimize out the contracts under the assumption that
\cppid{x} is \cppid{2}. 

However, if the build mode is set to \textmark{default}, the precondition at
\cppid{f()} would not be checked, but still assumed.  Consequently, after the
call to \cppid{f(val)} the compiler would be allowed to assume that \cppid{val}
is \cppid{2} and the preconditions of \cppid{g()} and \cppid{h()} would be
assumed to be correct and optimized out.  This would lead to undefined
behavior.  For calls to \cppid{h()} it might be the case that we got the
surprising effect that no function is called. But even worse, if the switch is
implemented as a jump table and the compiler assumes the contract and elides
the jump table bounds check, then a wild branch would arise.  The generated
code would attempt to read out-of-bounds at \cppid{\_\_jmptbl[val]},
reinterpret whatever bytes it finds there as an address of executable code, and
jump there to continue execution.  This would result in random code execution
and a very serious security issue.

\subsubsection{Avoiding unchecked assumptions with disabled continuation}

If we change the situation to require that no assumption of unchecked contract
can be made when the continuation is disabled, the outcome is quite different.

Compiling the code with the build mode set to \textmark{audit} would not be
problematic and would lead to the same outcome than with the current wording.

When the build mode is set to \textmark{default}, the precondition at
\cppid{f()} would not be checked and would not be assumed. Consequently, after
the call to \cppid{f(val)} no assumption can be made on the value of
\cppid{val}. The preconditions of \cppid{g()} and \cppid{h()} would not be
optimized out and the checks would be performed. No undefined behavior happens.

\subsubsection{Avoiding all assumptions with enabled continuation}

If we avoid all assumptions when continuation is enabled, we also avoid the
possible undefined behavior derived from assuming a failed contract.

\subsection{Example 2}

This example is a variation of previous example, which is also discussed
in~\cite{p1321r0}. In this variation the precondition at function \cppid{f()} is
now moved the be an axiom.

\begin{lstlisting}
void f(int x) [[expects axiom: x==2]]
{
  printf("%d\n", x);
}
\end{lstlisting}

With the current definition of contracts, axioms are always assumed.

When the build mode is set to \textmark{default}, the precondition at
\cppid{f()} would not be checked (as it is an axiom), but still assumed.
In this case, the contract elimination is considered to be intentional as
an axiom is considered to be always true.

When the build mode is set to \textmark{off}, no precondition is checked, but
\cppid{val==2} is still assumed. 

However, in some cases it might be interesting to be able to remove assumptions
introduced by axioms. That would be the case, in a debug version where the 
developer wants to remove all possible assumptions. On the other hand,
there are cases where axioms are desired to be used as assumptions.
We consider this aspect orthogonal to the checking level induced by the
build mode.

\subsection{Example 3}

Consider now this simple example:

\begin{lstlisting}
void f(int * p) [[expects axiom: p!=nullptr]]
{
  if (p) g();
  else h();
}
\end{lstlisting}

When axioms are assumed \cppid{f()} would be optimized to always call 
\cppid{g()}. 
That is not always desirable.
Again the ability to control independently  whether axioms are assumed or not
gives us what we need.

