\section{Observations on P1429R0}

\begin{frame}[t]{Semantics}
\begin{itemize}
  \item P1429R0 defines four semantics:
  \begin{itemize}
    \item \emph{ignore}.
    \item \emph{assume}.
    \item \emph{check-never-continue}.
    \item \emph{check-maybe-continue}. 
  \end{itemize}
  \vfill
  \item It proposes to be able to assign any semantic for any contract level.
    \begin{itemize}
      \item Leads to 32 combinations!
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Orhogonality}
\begin{itemize}
  \item Too much orthogonality is dangerous.
    \begin{itemize}
      \item Are things really orthogonal?
    \end{itemize}
  \vfill
  \item 32 combinations are not manageable.
    \begin{itemize}
      \item What are the implications for tools?
      \item How do I distribute my binaries?
      \item How do I manage complexity?
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Ignore}
\begin{itemize}
  \item Selective ingnorance is dangerous.
\end{itemize}
\begin{block}{Problem}
\begin{lstlisting}
void f(int * p)
  [[expects: p!=nullptr]]   //#1
  [[expects audit: *p>0]];  //#2
\end{lstlisting}
\end{block}
\begin{itemize}
  \item Options:
  \begin{itemize}
    \item Ignoring \#1 and \#2 is OK $\Rightarrow$ \emph{build-mode}=\cppid{off}.
    \item Checking \#1 and \#2 is OK $\Rightarrow$ \emph{build-mode}=\cppid{audit}.
    \item Checking \#1 and ignoring \#2 is OK \emph{build-mode}=\cppid{default}
    \item Ignoring \#1 and checking \#2 leads to \alert{UB}.
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Assume}
\begin{itemize}
  \item Excessive assumption leads to undefined behavior
  \vfill
  \item Don't forget:
    \begin{itemize}
      \item Beign able to assume a \cppkey{default} or \cppkey{audit} contract
            has considered a defect that triggered P1290.
      \item Assuming non-checked contracts may lead to removing other checks.
    \end{itemize}
  \vfill
  \item Options:
    \begin{itemize}
      \item Assuming \cppkey{default} or \cppkey{audit} contracts may lead to UB.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Continuation}
\begin{itemize}
  \item P1429R0 proposes two continuation semantics:
    \begin{itemize}
      \item \emph{check-never-continue}: Termination on violation.
      \item \emph{check-maybe-continue}: Continue after violation.      
    \end{itemize}

  \vfill
  \item Assigning continuation per level is not needed for gradual introduction
	  of contracts.
    \begin{itemize}
      \item Just use in code continuation when needed.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Equivalence}
\begin{itemize}
  \item All combinations in D1290R2 can be expressed through P1429R0:
    \begin{itemize}
      \item Axiom-mode=\cppid{off}, Build-mode=\cppid{off}.
        \begin{itemize}
	  \item \cppkey{axiom}=\emph{ignore}, 
		\cppkey{default}=\emph{ignore}, 
	        \cppkey{audit}=\emph{ignore}.
        \end{itemize}
      \item Axiom-mode=\cppid{on}, Build-mode=\cppid{off}.
        \begin{itemize}
	  \item \cppkey{axiom}=\emph{assume}, 
		\cppkey{default}=\emph{ignore}, 
	        \cppkey{audit}=\emph{ignore}.
        \end{itemize}
      \item Axiom-mode=\cppid{off}, Build-mode=\cppid{default}.
        \begin{itemize}
	  \item \cppkey{axiom}=\emph{ignore}, 
		\cppkey{default}=\emph{terminate}, 
	        \cppkey{audit}=\emph{ignore}.
        \end{itemize}
      \item Axiom-mode=\cppid{on}, Build-mode=\cppid{default}.
        \begin{itemize}
	  \item \cppkey{axiom}=\emph{assume}, 
		\cppkey{default}=\emph{terminate}, 
	        \cppkey{audit}=\emph{ignore}.
        \end{itemize}
      \item Axiom-mode=\cppid{off}, Build-mode=\cppid{audit}.
        \begin{itemize}
	  \item \cppkey{axiom}=\emph{ignore}, 
		\cppkey{default}=\emph{terminate}, 
	        \cppkey{audit}=\emph{terminate}.
        \end{itemize}
      \item Axiom-mode=\cppid{on}, Build-mode=\cppid{audit}.
        \begin{itemize}
	  \item \cppkey{axiom}=\emph{assume}, 
		\cppkey{default}=\emph{terminate}, 
	        \cppkey{audit}=\emph{terminate}.
        \end{itemize}
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Individual mapping considered harmful}
\begin{itemize}
  \item Individual mapping may lead to highly dangerous mappings.
\end{itemize}
\begin{lstlisting}
void f(int * p)
  [[expects: p!=nullptr]]
  [[expects audit: *p > 0]];
\end{lstlisting}
\begin{itemize}
  \item Consider:
    \begin{itemize}
      \item \cppkey{default}=check-maybe-continue, \cppkey{audit}=check-never-continue.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Levels versus modes}
\begin{itemize}
  \item P1429R0 allows to specify for a contract \textbf{either} a
	  \emph{contract-level} o \emph{contract-mode}.
    \begin{itemize}
      \item The only contract mode is \cppkey{check\_maybe\_continue}.
      \item Assumed to have a \cppkey{default} level.
      \item \alert{We cannot have audit continuing contracts!}.	      
    \end{itemize}

  \vfill
  \item D1290R2 proposes a \cppkey{continue} modifier.
    \begin{itemize}
      \item Can be applied to any \cppkey{default} or \cppkey{audit} contract.
      \item Generalization.
      \item Simplicity.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Other syntaxes}
\begin{itemize}
  \item A \emph{syntax-mode} for \cppkey{ignore}.
    \begin{itemize}
      \item Only syntax check!
      \item Not checked. Not assumed.
      \item Whats the point?
    \end{itemize}
\end{itemize}
\begin{lstlisting}
[[assert ignore: predicate()]];
\end{lstlisting}
\end{frame}

\begin{frame}[t,fragile]{Other syntaxes}
\begin{itemize}
  \item A \emph{syntax-mode} for \cppkey{assume}.
    \begin{itemize}
      \item Assumptions that cannot be disabled.
      \item But I want to debug with no optimizations!
    \end{itemize}
\end{itemize}
\begin{lstlisting}
[[assert assume: predicate()]];
\end{lstlisting}
\end{frame}

\begin{frame}[t,fragile]{Other syntaxes}
\begin{itemize}
  \item A \emph{syntax-mode} for \cppkey{check\_never\_continue}.
    \begin{itemize}
      \item Terminating checks that cannot be disabled.
      \item But I want to disable all checks in my super-release mode.
    \end{itemize}
\end{itemize}
\begin{lstlisting}
[[assert check_never_continue: predicate()]];
\end{lstlisting}
\end{frame}
